Project 1
====
**Group members: Fabiana Latorre, Oliver Benton Javier, Ernesto Canales, and Nikolaj Plagborg-Moller.**  
First, we load the four dataframes from the given URL.
```{r}
dfc <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from customers"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
dfo <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from orders"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
dfod <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from order_details"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
dfi <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from items"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
```
We then display the head of each dataframe.
```{r}
head(dfc)
head(dfi)
head(dfo)
head(dfod)
```
We now produce an interesting plot for each dataframe.
```{r}
ggplot(dfc, aes(x=CUSTOMER_STATE, y= CUSTOMER_CITY)) + geom_point()
``` 
  
We think it is interesting that there is a city called Fairfield in two states. How is that even possible! We do not know.
```{r}
ggplot(dfi, aes(x=ARTIST, y=UNIT_PRICE)) + geom_point()
```
  
We think it is interesting that the same artists charge somewhat similarly for their all their items.
```{r}
ggplot(dfo, aes(x=ORDER_DATE, y=CUSTOMER_ID)) + geom_point()
```
  
We think it is interesting that people order more things on some dates than other dates.
```{r}
ggplot(dfod, aes(x=ITEM_ID, y= ORDER_QTY)) + geom_point()
```
  
We think it is interesting that some items you would order more of at a time. But that is just us.
```{r} 
mega_set <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from orders o join customers c on o.customer_id = c.customer_id join order_details d on o.order_id = d.order_id join items i on d.item_id = i.item_id"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDB1.usuniversi01134.oraclecloud.internal', USER='DV_ORDERS', PASS='orcl', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
```
We now load the data frame into for the entire data set.
```{r}
p1 <- ggplot(mega_set, aes(x=as.Date(ORDER_DATE, "%Y-%m-%d"), y=as.Date(SHIPPED_DATE, "%Y-%m-%d"), color = as.factor(UNIT_PRICE))) + geom_point()
p1 + facet_wrap(~CUSTOMER_STATE)
```
We now produce the first plot. We used the as.Date and as.factor functionality. 
(Warnings stating missing values, we think that this are point that could not be plotted do to missing values in the database)
```{r}
p2 <- ggplot(mega_set, aes(x=as.Date(ORDER_DATE, "%Y-%m-%d"), y=as.Date(SHIPPED_DATE, "%Y-%m-%d"), color = as.factor(TITLE))) + geom_point()
p2 + facet_wrap(~CUSTOMER_STATE)
```
We now produce the second plot. 
(Warnings stating missing values, we think that this are point that could not be plotted do to missing values in the database)
```{r}
p3 <- ggplot(mega_set, aes(x=as.Date(ORDER_DATE, "%Y-%m-%d"), y=as.Date(SHIPPED_DATE, "%Y-%m-%d"), color = as.factor(ARTIST))) + geom_point()
p3 + facet_wrap(~CUSTOMER_STATE)
``` 
We now produce the third plot.(Warnings stating missing values, we think that this are point that could not be plotted do to missing values in the database)